---
title: "Create GovData and GovDataIND"
author: "Jose Luis Delgado Davara"
date: "5/21/2018"
output: html_document
---


This Rmarkdown is used to prepare the final files to send. This means:

1. Join vertically all the updated files --> INDupdates2018.csv and updates_2018.csv
2. Filter out the indicators without category assigned. From both IND and values files. (Drop.csv file)
3. Get the not-updated indicators and values from previous ingestion (GovData2017 and GovData2017IND)
4. Join vertically the files from (1) and (2) with the ones in (3)

```{r libraries, include=FALSE}
library(dplyr)
library(stringr)
```

# 1) Join Vertically updated files

```{r}
SOURCES2018 = c("BTI", "DB", "CPIA", "FH", "GCI", "IIAG", "ILO", "IPD", "IPU", "PEFA", "SC", "SGI", "TI", "WBL", "WGI", "WJP")

for (i in SOURCES2018){
  # Read files
  Route = paste0("1 Data cleaning/Cleaned files/",i,".csv")
  RouteIND = paste0("1 Data cleaning/Cleaned files/",i,"IND.csv")
  df = read.csv(Route, sep = ",")
  dfIND = read.csv(RouteIND, sep = ",")
     
  print(i)
  print(paste0("Number of columns imported in the .csv: ", ncol(df)))
  print(paste0("Number of columns imported in the IND.csv: ", ncol(dfIND)))
}  
```



```{r setup, include=FALSE}
SOURCES = c("BEEPS", "BTI", "CDG", "CPIA", "DB", "ES", "FAD_FR", "FH", "FSI", "GCI", "GFS", "Global_Indicators", "Global_Integrity", "HRM", "IBP", "IIAG", "ILO", "IPD", "IPU", "PAM", "PAM_IAD", "PAY_EMP", "PEFA", "PFI", "PIM", "PIV", "QOG", "SC", "SGI","TI", "WBL", "WGI", "WJP")
```
