---
title: "R Notebook"
output: html_notebook
---

```{r Reading files, include=FALSE}
library(dplyr)
# Read files
Data_Source = 'BTI'
file = paste("../Data/", Data_Source,"/", Data_Source, ".csv", sep = "")
df = read.csv(file, sep = ",")
fileIND = paste("../Data/", Data_Source,"/", Data_Source, "IND.csv", sep = "")
df_IND = read.csv(fileIND, sep = ",")

# Drop unused columns


dropIND = c("Rank", "Category_11",  "Category_12",  "Category_13", "Category_14", "Category_15",  "Category_21",  "Category_22", "Category_23", "Category_24" ,"Category_25", "Category_31", "Category_32", "Category_33", "Category_34",  "New1", "New2", "New3","New4", "New5", "keyN")
df_IND = df_IND[ ,!(names(df_IND) %in% dropIND)]
dim(df)

```

### Reading files

```{r}
plot(cars)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
